---
title: "Guides"
---

```{r, child="_setup.Rmd"}
```

<!-- TODO

- Create a guide:
  - to install and do basic git config (name and email)
  - clone the flc_website template

- Create a guide:
  - to create a GitHub account
  - create a github_pages repo
  - link an existing repository to gh_pages
  - push local webpage to github (publish site)
-->

# Installation

## Install R and RStudio {#install-r-rstudio}

[Getting started with R and RStudio](https://francojc.github.io/2017/08/14/getting-started-with-r-and-rstudio/)

## Install Git {#install-git}

Download and install the software from the `git` homepage. Follow this [link to the `git` downloads page](https://git-scm.com/downloads). 

```{r git-install-1, fig.cap='Git downloads page.', echo=FALSE}
display(readImage("images/git-install-1.png"))
```

Download the installer for you operating system and run this installer with the default installation recommendations.

Now that you have `git` on your machine, let's set some global options that will personalize your software while since we are already working at the command line. If you are on a Mac or Linux, open the 'Terminal'. If you are on a Windows machine, navigate to the programs menu and open 'git bash'. 

At the terminal, enter the following commands --replacing 'Your Name' and 'your\@email.com' with your information. 

```{bash, eval=FALSE, echo=TRUE}
git config --global user.name 'Your Name'
git config --global user.email 'your@email.com'
```
